### 2015-11-20 section/5_exper.tex
finish a pass of the whole paper

\begin{table}
  \centering
  \small
  \newcommand{\Yes}[1]{\checkmark{}$_#1$}
  \newcommand{\No}[0]{-}
  \begin{tabular}{lcccc}
    \toprule
                         &      	   &                        & {\bf Root}   &          \\
   {\bf BugID}           &  {\bf KLOC}     &  {\bf P. L.}           & {\bf Cause}  & {\bf Fix}\\
   \midrule
   Mozilla347306         & 88              & C                      &  0*1?        & C     \\
   Mozilla416628         & 105             & C                      &  0*1?        & C     \\
   Mozilla490742         &  -             & JS                     &  C-I         & B       \\
   Mozilla35294          &  -             & C++                    &  C-L         & B        \\ 
   Mozilla477564         &  -             & JS                     &  C-L         & M       \\
   \midrule 
   MySQL27287            & 995             & C++                    &  0*1?,C-L        & C     \\
   MySQL15811            & 1127            & C++                    &  C-L         & M \\ 
   \midrule    
   Apache32546           &  -             & Java                   &  C-I         & B  \\
   Apache37184           &  -             & Java                   &  C-I         & M  \\
   Apache29742           &  -             & Java                   &  C-L         & B \\ 
   Apache34464           &  -             & Java                   &  C-L         & M  \\
   Apache47223           &  -             & Java                   &  C-L         & B \\
   \midrule
   GCC46401              & 5521            & C                      &  [0$|$1]*    & S   \\
   GCC1687               & 2099            & C                      &  C-I         & M \\
   GCC27733              & 3217            & C                      &  C-I         & M \\
   GCC8805               & 2538            & C                      &  C-L         & B\\
   GCC21430              & 3844            & C                      &  C-L         & M \\
   GCC12322              & 2341            & C                      &  1*          & S\\
\bottomrule
   \end{tabular}
  %\nocaptionrule
  \caption{Benchmark information.
  (-: benchmarks extracted from real-world applications.
  ``C-I'': cross-iteration redundancy.
  ``C-L'': cross-loop redundancy.
  C, B, M, S: fix strategies as discussed in
  Table \ref{tab:root}.
  ) 
 }
  \label{tab:benchmarks}
\end{table}

@@

\paragraph{Metrics}
Our experiments are designed to evaluate \Tool from three main aspects:
\begin{itemize}
\item Coverage. Given our benchmark suite that covers a wide variety
of real-world root causes, can \Tool identify all those root causes?
\vspace{-0.05in}

\item Accuracy. 
When analyzing non-buggy loops, will \Tool generate any false positives?
\vspace{-0.05in}

\item Performance. 
What is the run-time overhead of \Tool?
\end{itemize}

\paragraph{Evaluation settings}
The imagined usage scenario of \Tool is that one will apply \Tool to identify
detailed root causes and provide fix-strategy suggestion for a small number of
suspicious loops that are most correlated with the specific performance problem.

Our evaluation uses existing statistical performance diagnosis
tool \cite{SongOOPSLA2014} to process a performance problem and identify 
one or a few suspicious loops for \Tool to analyze.
For 14 out of the 18 benchmarks, statistical performance debugging identifies the
real root-cause loop as the top ranked suspicious loop. For the remaining
benchmarks, the real root-cause loops are ranked number 2, 2, 4, and 10.
%Overall, we believe future tools can accurately identify the most one or a couple
%of suspicious loops.

@@

As discussed in Section \ref{sec:design}, our analysis contains 
several configurable thresholds. In our evaluation,
we use 0.001 as the \textit{resultless rate} threshold for identifying
0*1? loops, 0.01 as the \textit{resultless rate} threshold for identifying 
[0$|$1]* loops, 0.5 as the \textit{cross-loop redundancy rate}, and 
2 as the \textit{cross-iteration redundancy rate} (i.e., 
the number of distinct iterations is less than half of the total iterations).

@@

\subsection{Coverage Results}
\label{sec:coverage}
Overall, \Tool provides good diagnosis coverage, as shown in Table~\ref{tab:cover}. 
\Tool identifies the correct root cause for \textbf{all} 18 benchmarks, and 
suggests fix strategies that exactly match what developers took in practice
for 16 out of 18 cases. There are only two cases where \Tool fails to suggest
the fix strategy that developers used. For MySQL27287, the root-cause loop
is both cross-loop redundant and 0*1? inefficient. \Tool suggests both changing
data structures and memoization as fix strategies. In practice, the developers
find a new data structure that can eliminate both root causes.
For GCC12322, \Tool correctly tells that the loop under study
does not contain any form of inefficiency and produce results in every 
iteration, and hence fails to suggest any fix strategy. In practice, GCC
developers decide to skip the loop, which will cause some programs compiled by
GCC
to be less performance-optimal than before. However, GCC developers feel
that it is worthwhile considering the performance impact of the original loop
to the GCC compilation process.
Providing this type of
fix strategy suggestion goes beyond the capability of \Tool.

@@

\begin{table}
  \centering
  \small
  \newcommand{\Yes}[0]{\checkmark}
  \newcommand{\No}[0]{-}
  \begin{tabular}{lcccccc}
    \toprule
   {\bf BugID}           &  {\bf 0*1?}          &  {\bf [0$|$1]*}             &{\bf C-I$_b$}            &{\bf C-I$_m$}          &   {\bf C-L}     & {\bf Total}  \\
   \midrule
   Mozilla347306         &   -                  & -                           & -                       & -                     &   -             & -\\
   Mozilla416628         &   -                  & -                           & -                       & -                     &   -             & -\\
   Mozilla490742$_a$     &   -                  & -                           & -                       & -                     &   -             & -\\
   Mozilla35294$_a$      &   -                  & -                           & -                       & -                     &   -             & -\\ 
   Mozilla477564$_a$     &   -                  & -                           & -                       & -                     &   -             & -\\
   \midrule 
   MySQL27287            &   -                  & 0$_1$                       & -                       & -                     &   -             & 0$_1$\\
   MySQL15811            &   -                  & -                           & -                       & -                     &   -             & -\\ 
   \midrule    
   Apache32546           &   -                  & -                           & -                       & -                     &   -             & -\\
   Apache37184$_a$       &   -                  & -                           & -                       & -                     &   -             & -\\
   Apache29742$_a$       &   -                  & -                           & -                       & -                     &   -             & -\\ 
   Apache34464           &   -                  & -                           & -                       & -                     &   -             & -\\
   Apache47223           &   -                  & -                           & -                       & -                     &   -             & -\\
   \midrule
   GCC46401              &   -                  & 0$_1$                       & -                       & -                     &   -             & 0$_1$\\
   GCC1687               &   -                  & -                           & -                       & -                     &   -             & -\\
   GCC27733$_a$          &   -                  & -                           & -                       & -                     &   -             & - \\
   GCC8805               &   -                  & 0$_2$                       & -                       & -                     &   -             & 0$_2$\\
   GCC21430              &   0$_1$              & 0$_3$                       & -                       & 0$_1$                 &   0$_1$         & 0$_6$\\
   GCC12322              &   0$_1$              & 0$_1$                       & -                       & 0$_1$                 &   0$_1$         & 0$_4$\\
\bottomrule
   \end{tabular}
  %\nocaptionrule
  \caption{False positives of \Tool, when applying to top 5 loops reported by 
    statistical performance diagnosis for each benchmark. `-': no false positive. $x_y$: $x$ real false positives and $y$ benign ones.
}
  \label{tab:top5}
\end{table}

@@

The accuracy of \Tool benefits from its run-time analysis.
For example, 4 benchmarks contain loops that only generate side-effect
in the last iteration among their top 5 suspicious loops. However,
these loops are actually not inefficient because the portion of
resultless iterations is small. 
%TODO a table 6 was deleted from oopsla submission

The good accuracy of \Tool can actually help improving the accuracy of
identifying which loop is the root cause loop.
For example, the real root-cause loop of Apache34464 and GCC 46401 both
rank number two by the statistical performance diagnosis tool.
\Tool can tell that the number one loops in both cases do not contain
any form of inefficiency, resultless or redundancy. This result can
potentially used to improve the accuracy of identifying root cause loops.

@@

\begin{table}
  \centering
  \scriptsize
  \newcommand{\Yes}[1]{\checkmark{}$_#1$}
  \newcommand{\No}[0]{-}
  \begin{tabular}{lccccc}
    \toprule
	    & \multicolumn{3}{c}{\Tool w/ optimization} & \multicolumn{2}{c}{w/o optimization} \\
     \cmidrule(lr){2-4}
     \cmidrule(lr){5-6}
     {\bf BugID}  & {\bf Resultless}  &  {\bf C-L R. } & {\bf C-I R. }  & {\bf C-L R.}  & {\bf C-I R. } \\
    \midrule
    Mozilla347306 &  1.07\%           &  22.40\%       &  10.17\%       & 304.37{\bf X} & 468.74{\bf X} \\ 
    Mozilla416628 &  0.80\%           &  4.10\%        &  2.99\%        & 567.51{\bf X} & 85.6{\bf X} \\
    \midrule
     MySQL27287   & $\sim$0           &   1.66\%       &   -            & 109.55{\bf X} & 352.07{\bf X} \\
     MySQL15811   &  -                &   0.03\%       &   -            & 227.04{\bf X} & 424.44{\bf X} \\
    \midrule
      GCC46401    & 3.12\%         & 3.80\%            &  5.95\%        & 21.07{\bf X}  & 38.44{\bf X}\\ 
      GCC1687     & -              & /                 &  $\sim$0       &   /           & 142.29{\bf X} \\
      GCC27733$_a$    & $\sim$0        & /                 &  4.73\%        &   /           & 17.41{\bf X}     \\
      GCC8805     & -              & $\sim$0           & $\sim$0        & 2.22{\bf X}   &  3.52{\bf X}\\
      GCC21430    & -              & 5.46\%            &   0.69\%       & 107.20{\bf X} & 159.89{\bf X} \\
      GCC12322    & -              & 1.75\%            &  $\sim$0       & 21.07{\bf X}  & 38.44{\bf X} \\
   \bottomrule
   \end{tabular}
  %\nocaptionrule
  \caption{Run-time overhead of applying \Tool to the buggy loop
    (only non-extracted benchmarks are shown). 
  -: dynamic analysis is not conducted, as static analysis is sufficient.
  /: not applicable.}
  \label{tab:performance}
\end{table}

@@

As shown in Table \ref{tab:performance}, 
the performance of \Tool is good. The overhead is consistently under or around 5\% 
except for one benchmark, Mozilla347306. We believe \Tool is promising for potential production
run usage. Of course, if we apply \Tool to multiple loops simultaneously,
the overhead will be higher. However, the current results are obtained by running the
program only \textbf{once} under the problem-triggering workload. The sampling nature
of \Tool will allow us to keep the overhead low at the exchange of running the program for
a couple of more times, if needed.

As we can also see from the table, our performance optimization discussed in 
Section \ref{sec:inst} and \ref{sec:perf} has contributed
a lot to the good performance of \Tool.

Without sampling, while still applying our static optimization, our redundancy
analysis would lead to over 100X slowdown for five benchmarks.

The buggy loops of MySQL\#27287 and MySQL\#15811 access arrays. 
After changing to tracking the initial and ending memory-access addresses
of the array, instead of the content of the whole array accesses,
the overhead is reduced from 11.77\% to 1.66\% for MySQL\#27287, 
and from 20.46\% to 0.03\% for MySQL\#15811 respectively 
(sampling is conducted consistently here).

The side-effect of the buggy loop for MySQL15811 is to calculate the length of a string. 
The variable representing the length is an induction variable. 
The side-effect of the buggy loop for MySQL27287 is to calculate the index of a searched target, 
and the variable representing the index is also an induction variable. 
We can reply on static analysis to figure out that these two loops are not cross-iteration redundant.

We also tried sampling with different sampling rates.
For cross-loop redundancy, we also conduct experiments under sampling rate 1
out of 1000. 
Both run-time overhead and collected sample will be reduced. Mozilla347306 
is still the benchmark with largest overhead, but the overhead is reduced to 0.49\%. For two benchmarks, GCC8805 and GCC12322, we cannot sample 
more than 10 loop instances and hence cannot draw strong conclusion
about their root-cause type. For all other benchmarks, we can 
still have more than 10 loop instances and get exactly the same 
root-cause analysis results presented above.

We also conduct cross-iteration redundant experiment under different sampling rates. When the sampling rate is 1 out of 100, there are two benchmarks, whose runtime overhead is larger than 30\%. The overhead for Mozilla347306 is 59.57\%, 
and the overhead of GCC21430 is 30.65\%. When changing sampling rate to 1
out of 10000, Mozilla347306 has the largest overhead, which is 4.47\%. And mozilla347306 is the only one whose overhead is larger than 2\%. Except for 
GCC12322, all other benchmarks will have more than 100 iterations sampled, under the sample rate is 1 out of 10000. Consequently, the same root-cause
analysis results will be reported for these benchmarks as the ones presented
above.

>>>>

\begin{table}
  \centering
  \small
  \newcommand{\Yes}[1]{\checkmark{}$_#1$}
  \newcommand{\No}[0]{-}
  \begin{tabular}{lcccc}
    \toprule
   {\bf BugID}           &  {\bf KLOC}     &  {\bf P. L.}           & {\bf RootCause}  & {\bf Fix}\\
   \midrule
   Mozilla347306         & 88              & C                      &  0*1?        & C     \\
   Mozilla416628         & 105             & C                      &  0*1?        & C     \\
   Mozilla490742         &  -             & JS                     &  C-I         & B       \\
   Mozilla35294          &  -             & C++                    &  C-L         & B        \\ 
   Mozilla477564         &  -             & JS                     &  C-L         & M       \\
   \midrule 
   MySQL27287            & 995             & C++                    &  0*1?,C-L        & C     \\
   MySQL15811            & 1127            & C++                    &  C-L         & M \\ 
   \midrule    
   Apache32546           &  -             & Java                   &  C-I         & B  \\
   Apache37184           &  -             & Java                   &  C-I         & M  \\
   Apache29742           &  -             & Java                   &  C-L         & B \\ 
   Apache34464           &  -             & Java                   &  C-L         & M  \\
   Apache47223           &  -             & Java                   &  C-L         & B \\
   \midrule
   GCC46401              & 5521            & C                      &  [0$|$1]*    & S   \\
   GCC1687               & 2099            & C                      &  C-I         & M \\
   GCC27733              & 3217            & C                      &  C-I         & M \\
   GCC8805               & 2538            & C                      &  C-L         & B\\
   GCC21430              & 3844            & C                      &  C-L         & M \\
   GCC12322              & 2341            & C                      &  1*          & S\\
\bottomrule
   \end{tabular}
  %\nocaptionrule
  \caption{Benchmark information.
  (-: benchmarks extracted from real-world applications.
  ``C-I'': cross-iteration redundancy.
  ``C-L'': cross-loop redundancy.
  C, B, M, S: fix strategies as discussed in
  Table \ref{tab:root}.
  ) 
 }
  \label{tab:benchmarks}
\end{table}

@@

\paragraph{Metrics}
Our experiments are designed to evaluate \Tool from three main aspects:
(1) 
\textit{Coverage}. Given our benchmark suite that covers a wide variety
of real-world root causes, can \Tool identify all those root causes?
(2)
\textit{Accuracy}. 
When analyzing non-buggy loops, will \Tool generate any false positives?
(3) 
\textit{Performance}.
What is the run-time overhead of \Tool?

\paragraph{Evaluation settings}
Our evaluation uses existing statistical performance diagnosis
tool \cite{SongOOPSLA2014} to process a performance problem and identify 
one or a few suspicious loops for \Tool to analyze.
For 14 out of the 18 benchmarks, statistical debugging identifies the
real root-cause loop as the most suspicious loop. For the remaining
benchmarks, the real root-cause loops are ranked number 2, 2, 4, and 10.
%Overall, we believe future tools can accurately identify the most one or a couple
%of suspicious loops.

@@

As discussed in Section \ref{sec:design}, our analysis contains 
several configurable thresholds. In our evaluation,
we use 0.001 as the \textit{resultful rate} threshold for identifying
0*1? loops, 0.01 as the \textit{resultful rate} threshold for identifying 
[0$|$1]* loops, 0.5 as the \textit{cross-loop redundancy rate}, and 
2 as the \textit{cross-iteration redundancy rate} (i.e., 
the number of distinct iterations is less than half of the total iterations).

@@

More discussions about all the parameters/thresholds presented above, including
how to set them and how sensitive they are, are discussed in Section
\ref{sec:sensi}.

\subsection{Coverage Results}
\label{sec:coverage}
Overall, \Tool provides good diagnosis coverage, as shown in Table~\ref{tab:cover}. 
\Tool identifies the correct root cause for \textbf{all} 18 benchmarks, and 
suggests fix strategies that exactly match what developers took in practice
for 16 out of 18 cases. There are only two cases where \Tool fails to suggest
the fix strategy that developers used. For MySQL27287, the root-cause loop
is both cross-loop redundant and 0*1? inefficient. \Tool suggests both changing
data structures and memoization as fix strategies. In practice, the developers
find a new data structure that can eliminate both root causes.
For GCC12322, \Tool correctly tells that the loop under study
does not contain any form of inefficiency and produce results in every 
iteration, and hence fails to suggest any fix strategy. In practice, GCC
developers decide to skip the loop, which will cause some programs compiled by
GCC
to be less performance-optimal than before. However, GCC developers feel
that it is worthwhile considering the slow-down caused by the original loop.

@@

\begin{table}
  \centering
  \small
  \newcommand{\Yes}[0]{\checkmark}
  \newcommand{\No}[0]{-}
  \begin{tabular}{lcccccc}
    \toprule
   {\bf BugID}           &  {\bf 0*1?}          &  {\bf [0$|$1]*}             &{\bf C-I$_b$}            &{\bf C-I$_m$}          &   {\bf C-L}     & {\bf Total}  \\
   \midrule
   Mozilla347306         &   -                  & -                           & -                       & -                     &   -             & -\\
   Mozilla416628         &   -                  & -                           & -                       & -                     &   -             & -\\
   Mozilla490742$_a$     &   -                  & -                           & -                       & -                     &   -             & -\\
   Mozilla35294$_a$      &   -                  & -                           & -                       & -                     &   -             & -\\ 
   Mozilla477564$_a$     &   -                  & -                           & -                       & -                     &   -             & -\\
   \midrule 
   MySQL27287            &   -                  & 0$_1$                       & -                       & -                     &   -             & 0$_1$\\
   MySQL15811            &   -                  & -                           & -                       & -                     &   -             & -\\ 
   \midrule    
   Apache32546           &   -                  & -                           & -                       & -                     &   -             & -\\
   Apache37184$_a$       &   -                  & -                           & -                       & -                     &   -             & -\\
   Apache29742$_a$       &   -                  & -                           & -                       & -                     &   -             & -\\ 
   Apache34464           &   -                  & -                           & -                       & -                     &   -             & -\\
   Apache47223           &   -                  & -                           & -                       & -                     &   -             & -\\
   \midrule
   GCC46401              &   -                  & 0$_1$                       & -                       & -                     &   -             & 0$_1$\\
   GCC1687               &   -                  & -                           & -                       & -                     &   -             & -\\
   GCC27733$_a$          &   -                  & -                           & -                       & -                     &   -             & - \\
   GCC8805               &   -                  & 0$_2$                       & -                       & -                     &   -             & 0$_2$\\
   GCC21430              &   0$_1$              & 0$_3$                       & -                       & 0$_1$                 &   0$_1$         & 0$_6$\\
   GCC12322              &   0$_1$              & 0$_1$                       & -                       & 0$_1$                 &   0$_1$         & 0$_4$\\
\bottomrule
   \end{tabular}
  %\nocaptionrule
  \caption{False positives of \Tool for top 5 loops reported by 
    statistical debugging for each benchmark. `-': no false positive. $x_y$: real ($x$) and benign false positives ($y$).
}
  \label{tab:top5}
\end{table}

@@

The accuracy of \Tool benefits from its run-time analysis.
For example, there are seven benchmarks in total that each contains
one loop, which generates side effect only
in its last iteration. Without run-time information, \Tool would judge
all of them as inefficient (i.e., 0*1? resultless). Fortunately,
\Tool run-time analysis counts the total number of loop iterations and
correctly identifies three of them as truly inefficient and severe enough
to cause the corresponding performance problem.
%TODO a table 6 was deleted from oopsla submission

\Tool can also help improve the accuracy of statistical debugging in
identifying which loop is the root cause loop.
For example, the real root-cause loop of Apache34464 and GCC 46401 both
rank number two by the statistical performance diagnosis tool.
Fortunately,
\Tool can tell that the number one loops in both cases do not contain
any form of inefficiency, resultless or redundancy.

@@

\begin{table}
  \centering
  \scriptsize
  \newcommand{\Yes}[1]{\checkmark{}$_#1$}
  \newcommand{\No}[0]{-}
  \begin{tabular}{lccccc}
    \toprule
	    & \multicolumn{3}{c}{\Tool w/ optimization} & \multicolumn{2}{c}{w/o optimization} \\
     \cmidrule(lr){2-4}
     \cmidrule(lr){5-6}
     {\bf BugID}  & {\bf Resultless}  &  {\bf C-L R. } & {\bf C-I R. }  & {\bf C-L R.}  & {\bf C-I R. } \\
    \midrule
    Mozilla347306 &  1.07\%           &  22.40\%       &  10.17\%       & 304.37{\bf X} & 468.74{\bf X} \\ 
    Mozilla416628 &  0.80\%           &  4.10\%        &  2.99\%        & 567.51{\bf X} & 85.6{\bf X} \\
    \midrule
     MySQL27287   & $\sim$0           &   1.66\%       &   -            & 109.55{\bf X} & 352.07{\bf X} \\
     MySQL15811   &  -                &   0.03\%       &   -            & 227.04{\bf X} & 424.44{\bf X} \\
    \midrule
      GCC46401    & 3.12\%         & 3.80\%            &  5.95\%        & 21.07{\bf X}  & 38.44{\bf X}\\ 
      GCC1687     & -              & /                 &  $\sim$0       &   /           & 142.29{\bf X} \\
      GCC27733$_a$    & $\sim$0        & /                 &  4.73\%        &   /           & 17.41{\bf X}     \\
      GCC8805     & -              & $\sim$0           & $\sim$0        & 2.22{\bf X}   &  3.52{\bf X}\\
      GCC21430    & -              & 5.46\%            &   0.69\%       & 107.20{\bf X} & 159.89{\bf X} \\
      GCC12322    & -              & 1.75\%            &  $\sim$0       & 21.07{\bf X}  & 38.44{\bf X} \\
   \bottomrule
   \end{tabular}
  %\nocaptionrule
  \caption{Run-time overhead of applying \Tool to the buggy loop
    (only non-extracted benchmarks are shown). 
  -: dynamic analysis is not needed;
  /: not applicable.}
  \label{tab:performance}
\end{table}

@@

As shown in Table \ref{tab:performance}, 
the performance of \Tool is good. The overhead is consistently under or around 5\% 
except for one benchmark, Mozilla347306. We believe \Tool is promising for potential production
run usage.
We can easily further lower the overhead through sparser sampling.
As we will discuss later, 
the current diagnosis results are obtained by running the
program only \textbf{once} under the problem-triggering workload.
If we use sparser sampling, more failure runs will be needed to obtain good
diagnosis results.

As we can also see from the table, our performance optimization discussed in 
Section \ref{sec:inst} and \ref{sec:perf} has helped.

The performance benefit of sampling is huge.
Without sampling, even with all the static optimization, redundancy
analysis lead to over 100X slowdown for five benchmarks.

The benefit of static optimization is also non-trivial. 
For example, for MySQL15811 and MySQL27287, static analysis alone can
judge that they do not contain cross-iteration redundancy: the computation of 
each iteration depends on loop induction variables, which are natually different
in different iterations. Consequently, run-time overhead is completely
eliminated for these two benchmarks.
As another example, the buggy loops of MySQL\#27287 and MySQL\#15811 access 
arrays. 
After changing to tracking the initial and ending memory-access addresses
of the array, instead of the content of the whole array accesses,
the overhead is reduced from 11.77\% to 1.66\% for MySQL\#27287, 
and from 20.46\% to 0.03\% for MySQL\#15811 respectively 
(sampling is conducted consistently here).

\subsection{Parameter Setting and Sensitivity}
\label{sec:sensi}
\paragraph{Sampling rates}
We have tried different sampling rates for redundancy analysis.
Intuitively, sparser sampling leads to lower overhead but worse diagnosis
results. Due to space constraints, we briefly summarize the results below.

When we lower the sampling rate from 1/100 to 1/1000 
in cross-loop redundancy analysis,
Mozilla347306 still incurs the largest overhead (0.49\%). 
The diagnosis results remain the same for all but
GCC8805 and GCC12322, where too few samples are available
to judge redundancy.

When we lower the sampling rate from 1/1000 to 1/10000
in cross-iteration redundancy analysis,
Mozilla347306 has the largest overhead (4.47\%). 
%In fact, Mozilla347306 is the only one whose overhead is larger than 2\%. 
The diagnosis results remain 
the same for all but GCC12322.
%If we increase the sampling rate to 1/100, we will 
%have two benchmarks whose overhead is larger than 30\%.

\paragraph{Resultful and redundancy rate}
Since the severity of resultless and redundant loops depends on
workload, it is natural that \Tool uses thresholds in its diagnosis.
Intuitively, changing these thresholds affects the
false positive and false negative of \Tool. For example, 
if we change the cross-iteration redundancy rate from the default 2
to 4, \Tool incurs 1 more false negative and 1 fewer false positive.

Our default setting is obtained based on our experience
and should work for many problems.
Developers can adjust these thresholds based on their
need. They can even get rid of all threshods, and only
use the raw values of resultful/redundancy rates to understand
the absolute and relative resultless/redundancy nature of suspicious 
loops.

### 2015-11-20 section/6_related.tex
finish a pass of the whole paper

Recently, tools that go beyond profiling and provide more automated analysis
have been proposed.
StackMine~\cite{Han:2012:PDL:2337223.2337241} can
identify slow call-stack patterns inside event handlers. The work by
\citet{TaoAsplos2014} analyzes system traces to understand 
performance impact propagation and 
causality relationship among different system components. 
X-ray~\cite{Attariyan:2012:XAR:2387880.2387910} helps identify inputs
or configuration entries that are most responsible for performance problems.
Although these techniques are all very useful, 
they target different problems from \Tool. \Tool targets 
inefficient loops, a common
inefficiency problem that contributes to
about two thirds of real-world user-perceived performance problems studied
by previous work \cite{SongOOPSLA2014}, and tries to pin-point the exact
root cause and provide fix-strategy suggestions.

\Tool is most related to
the recent statistical performance debugging work
\citep{SongOOPSLA2014}, both trying to identify source-code level root causes
for user-perceived performance problems. 
This previous work identifies which loop is most correlated with 
a performance symptom through statistical analysis, 
but cannot answer whether or 
what type of inefficiency this loop contains.
\Tool complements it by
providing detailed root cause information and fix strategy suggestions through
program analysis.

@@

As discussed in 
Section \ref{sec:intro}, these tools are all useful in improving software
performance, but are not suitable for performance diagnosis.
With different design goals from \Tool, these bug detection tools are not 
guided by any specific
performance symptoms. Consequently, they take different coverage-accuracy
trade-offs from \Tool. \Tool tries to cover a wide variety of root-cause 
categories and is more aggressive in identifying root-cause categories, because
it is only applied to a small number of loops that are known to be highly
correlated with the specific performance symptom under study.
Performance-bug detection tools has to be more conservative and tries hard
to lower false positive rates, because it needs to apply its analysis to the
whole program, instead of just a few loops. This requirement causes bug
detection tools to each focus on a specific root-cause category.
%In fact, most inefficient loops in our study are very difficult to be detected
%by a generic performance bug detectors --- it is very difficult to prove them to
%be inefficient without application-specific domain knowledge.
%For example, only a couple of inefficient loops out of the 45 studied
%in Table \ref{tab:root} can be detected by recent static inefficient
%loop checkers
%\cite{CARAMEL,IsilDillig.PLDI15}.
Performance bug detection tools also do not aim to provide fix suggestions.
For the few that do provide \cite{CARAMEL}, they only focus on very specific
fix patterns, such as adding a break into the loop. 
In addition, dynamic performance bug detectors do not try to achieve any
performance goals. None of them has tried applying sampling to their
bug detection and often leads to 10X slowdowns or more.

>>>>

Recently, tools that go beyond profiling and provide more automated analysis
have been proposed.
StackMine~\cite{Han:2012:PDL:2337223.2337241} 
identifies slow call-stack patterns inside event handlers. The work by
\citet{TaoAsplos2014} analyzes system traces to understand 
performance impact propagation and 
causality relationship among system components. 
X-ray~\cite{Attariyan:2012:XAR:2387880.2387910} helps identify inputs
or configuration entries that are most responsible for performance problems.
Coz~\cite{coz.sosp15} can estimate the performance impact of any
potential optimization at any point of a multi-threaded program.
Although these techniques are all very useful, 
they target different problems from \Tool. 
\comment{
\Tool targets 
inefficient loops, a common
inefficiency problem that contributes to
about two thirds of real-world user-perceived performance problems studied
by previous work \cite{SongOOPSLA2014}, and tries to pin-point the exact
root cause and provide fix-strategy suggestions.
}

\Tool is most related to
the recent statistical performance debugging work
\citep{SongOOPSLA2014}, both trying to identify source-code level root causes
for user-perceived performance problems. 
This previous work identifies which loop is most correlated with 
a performance symptom through statistical analysis, 
but cannot answer whether or 
what type of inefficiency this loop contains.
\Tool complements it by
providing detailed root cause information and fix strategy suggestions.

@@

As discussed in 
Section \ref{sec:intro}, these tools are all useful in improving software
performance, but are not suitable for performance diagnosis.
With different design goals from \Tool, these bug detection tools are not 
guided by any specific
performance symptoms. Consequently, they take different coverage-accuracy
trade-offs from \Tool. \Tool tries to cover a wide variety of root-cause 
categories and is more aggressive in identifying root-cause categories, because
it is only applied to a small number of loops that are known to be highly
correlated with the specific performance symptom under study.
Performance-bug detection tools has to be more conservative and tries hard
to lower false positive rates, because it needs to process the
whole program, instead of just a few loops. This requirement causes bug
detection tools to each focus on a specific root-cause category.
%In fact, most inefficient loops in our study are very difficult to be detected
%by a generic performance bug detectors --- it is very difficult to prove them to
%be inefficient without application-specific domain knowledge.
%For example, only a couple of inefficient loops out of the 45 studied
%in Table \ref{tab:root} can be detected by recent static inefficient
%loop checkers
%\cite{CARAMEL,IsilDillig.PLDI15}.
Performance bug detection tools also do not aim to provide fix suggestions.
For the few that do provide \cite{CARAMEL}, they only focus on very specific
fix patterns, such as adding a break into the loop. 
In addition, dynamic performance bug detectors do not try to achieve any
performance goals. None of them has tried applying sampling to their
bug detection and often leads to 10X slowdowns or more.
